Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-10 fplc-elic.tex
post-meeting notes and fixes

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\begin{definition}
  Let properties $\Gamma:\P\toto\R$ and $\Gamma':\P\toto\R'$ be given.
  The function $f:\R'\to\R$ is a \emph{selective link function} if (i) $r'\in\Gamma'(p) \implies f(r') \in \Gamma(p)$, and (ii) $f(\Gamma'(p)) = \Gamma(p)$.
  The function $f:\R'\toto\R$ is an \emph{exhaustive link function} if $r'\in\Gamma'(p) \iff f(r') = \Gamma(p)$.
  \raf{I think I got these right, but definitely need to check}
\end{definition}

@@

\begin{definition}
  Elicitation complexity of $\Gamma:\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
\end{definition}

@@

\begin{definition}
  Let $\gamma:\P\toto\R$.
  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \iff \varphi(r') \in \gamma(p)$.
\end{definition}
\raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}

\raf{What can we say about the link function $f:\reals^d\to\R$ in the above case?  Do we need the following proposition to construct a selective link?  Perhaps the definition of embedding should be all about the link...}

>>>>

% alphabetical order, by convention
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\begin{definition}
  Let properties $\gamma:\P\toto\R$ and $\Gamma:\P\toto\V$ be given.
  The function $f:\V\to\R$ is a \emph{selective link function} if (i) $v\in\Gamma(p) \implies f(v) \in \gamma(p)$, and (ii) $f(\Gamma(p)) = \gamma(p)$.
  The function $f:\V\toto\R$ is an \emph{exhaustive link function} if $v\in\Gamma(p) \iff f(v) = \gamma(p)$.
\end{definition}

@@

\raf{If we want to state this general definition for posterity; won't be needed.}
\begin{definition}
  Elicitation complexity of $\gamma:\P\toto\R$... min dimension of $\Gamma\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\gamma$.
  \raf{Maybe break into ``selective'' and ``exhaustive'' versions?}
\end{definition}

@@

\begin{definition}
  Let $\gamma:\P\toto\R$.
  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  \raft{Note: definition is general and not specific to FPLC, finite propertes, etc.}
\end{definition}

\begin{lemma}
  \label{lem:embed-lev-set-subset}
  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, then for all $v\in\reals^d$, we have $\Gamma_v \subseteq \gamma_r$ for some $r\in\R$.
\end{lemma}

\begin{proposition}
  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, there is a selective link $f:\reals^d\to\R$ from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
  Let $\V = \bigcap\{ \Gamma(p) : p\in\P\} \subseteq \reals^d$ be the image of $\Gamma$.
  Define $F:\V\toto\R$ as follows: $F(v) = \bigcap\{\gamma(p) : v\in\Gamma(p)\} = \bigcap\{\gamma(p) : p \in\Gamma_v\}$.
  That is, $F$ encodes all reports of $\gamma$ which could be correct when $v$ is chosen from $\Gamma$.
  Now let $v\in\V$, and let $r\in\R$ be given by Lemma~\ref{lem:embed-lev-set-subset}, so that $\Gamma_v \subseteq \gamma_r$.
  Then $p\in\Gamma_v \implies r\in\gamma(p)$, so we have $r \in F(v)$, and in particular, $F(v)\neq\emptyset$.
  (The latter would be vacuous if there were no $p\in\Gamma_v$, but we have assumed so by definition of $\V$.)
  We simply define $f:\reals^d$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
  (This is a consistent choice by definition of $\varphi$.)

  It remains to show that $f$ is a selective link.
  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
  For (ii), let $p$ be given.
  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
  By (i), this must be an equality.
\end{proof}
